### 2017-01-10 paper/evaluation.tex
pass on RQ3

To evaluate the presence of parallelization settings (see Section
\ref{sec:modes}), we considered the \numMedLong{} subjects from the
\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
focused in these two groups because given that costly test suites
exist, we investigated if the maintainers are aware of parallelization
settings.

\Jbc{methodology is poorly described...}
\Fix{
We computed the frequency of the
parallelism modes using a two-steps approach: the first step
(discovery) automatically finds relevant build files (\ie, \pomf{}
files with parallelization settings); the second step (inspection)
consists in a manual inspection to confirm the presence of parallelism
settings in the build file and classify them according to the
parallelism level.  Figure \Fix{removed}
describes the discovery step: we list the paths of all build files and
filter only the files that contain any of the keywords
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.  Notice
that, for Maven projects, any of these keywords exist in any possible
parallel setting \Fix{cite surefire doc}. Our first step is complete
but is not sound since the line that matches one of keywords may not
represent part of a real setting (\eg, comments).  We eliminate
false-positives in the confirmation step.
}

\newcommand{\pomMedLong}{2851}

\Jbc{results from table}From the \numMedLong{} subjects, we found
\pomMedLong{} \pomf{} files and selected the 109 files that matched
with any of the configuration keywords (\ie, \CodeIn{forkCount},
\CodeIn{forkMode}, and \CodeIn{parallel}).  From these 109 build
files, we eliminated six false-positives: two were names of project
modules (\eg, \emph{camel-cookbook-parallel-processing}); one was part
of a comment; three were commented configurations. The 106 build files
with valid configurations are distributed in 41 projects from our
sample.  Table~\ref{tab:inspection-table} summarizes our results.

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  (false-positives) &       / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
        \midrule%
        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallel configurations in build files from
    projects with time-consuming tests. \Fix{explain columns}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} projects\Jbc{Currently medium and partially
    the long group...}}
\end{figure}

@@

>>>>

To evaluate the presence of parallelization settings (see Section
\ref{sec:modes}), we considered all projects classified as \medg{} and
\longg{}-running, a total of \numMedLong{} subjects (see
Figure~\ref{fig:rq1-barplot}). To reduce noise we did not consider
projects with \shortg{}-running test suites as we observed\Mar{please,
  confirm} that those projects often\Mar{adjust} do not use
parallelism; including them would favor sequential execution in our
analysis.

%% We
%% focused in these two groups because given that costly test suites
%% exist, we investigated if the maintainers are aware of parallelization
%% settings.

To answer RQ3\Mar{use macro} we initially mined build files (\ie,
\pomf{}) that contain parallelization keywords, namely
\CodeIn{forkMode}, \CodeIn{forkCount}, and \CodeIn{parallel}.
According to the Maven surefire documentation\Fix{cite surefire doc},
any configuration to run tests in parallel must contain one of these
keywords. This mining step, however, is not sound as a matching
project may not indicate a project with a valid configuration for
running tests in parallel.  False positive can happen because of
comments, for instance.  To eliminate the cases of false positives and
also to categorize true positive cases, we complemented the initial
mining step with a manual inspection of files.

%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

Figure~\ref{tab:inspection-table} summarizes our results.  Column
``Group'' indicates the group of projects according to their time
cost.\Mar{quickly explain other columns}

%% summarize observations...
From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where 109\Mar{use macro} of those files match one of the keywords
mentioned above.  From these 109\Mar{use macro} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The 106\Fix{fix
  this} build files with valid configurations are distributed across
41\Mar{use macro} projects from our sample.  \emph{From these results
  we found that $\sim$51\% of medium and long-running projects do not
  use parallel features to run test suites.}\Mar{please make it
  consistent with research question}\Mar{explain this is
  over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  (false-positives) &       / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
        \midrule%
        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallel configurations in build files from
    projects with time-consuming tests. \Fix{explain columns}}
    \label{tab:inspection-table} 
\end{figure}

\subsubsection{Distribution of parallel modes}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} projects\Jbc{Currently medium and partially
    the long group...}}
\end{figure}
